\section{Pick Up Sticks!}
	\sectionstart{The first game}{The most accurately named game of all time.}
	\begin{namedframe}{Rules and intro}
		\alert{Pick up sticks} is a 2 player game that is often used as a game theory question on math contests. The game involves:

		\sep

		Starting with $n$ sticks, the players take turns taking up to $k$ sticks from the total number of sticks until there are none left.

		\sep

		Variations include the winner being the one who takes the last stick, or the loser being the one who takes the last stick.

		\sep

		The game can be structured in such ways that certain players can win every time. Let’s look at some of these scenarios!
	\end{namedframe}
	\begin{namedframe}{The scenarios: your worksheet}
		Let's go over some scenarios.
		\begin{description}[<+(1)->]
			\item[Scenario 1] Whoever picks the last stick \emph{loses}. Which player can guarantee a win?
			\vertspace
			There are 24 sticks in total, and the players can take up to 4 sticks.

			\item[Scenario 2] Whoever picks the last stick \emph{wins}. Which player can guarantee a win?
			\vertspace
			There are 35 sticks, and the players can take up to 4 sticks on their turns.
		\end{description}
	\end{namedframe}
	\bigframe{Try it out yourself!}
	\begin{namedframe}{Answers: The Strats}
		Let's take those scenarios up together.
		\begin{description}[<+(1)->]
			\item[Scenario 1] Player 1 always wins. Why?
			\item[Scenario 2] Player 2 always wins. Why?
		\end{description}
	\end{namedframe}
