\input{../WorksheetPreamble.tex}

\usepackage{cleveref}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{angles,quotes}
\usetkzobj{all}

\title{Euclid Preparation 4}
\author{Mackenzie Math Club}
\date{March 26, 2017}

\rfoot{\parbox[t]{0.35\textwidth}{\copyright{} Lev Raizman, 2018}} 

\begin{document}
	\paragraph{Direct Proofs} These proofs rely on only axioms, definitions, and other proven theorems.\\
	\begin{enumerate}
		\item Prove that the sum of two even integers is even. Prove that the sum of two odd integers is odd.\solutionspace{2cm}
		\item Prove that $a^5+b^5=(a+b)(a^4-a^3b+a^2b^2-ab^3+b^4)$. \solutionspace{3cm}
	\end{enumerate}
	\hrule
	\paragraph{Proof by Contradiction} These proofs rely on making a wrong assumption, and then showing that the assumption must be false.
	\begin{enumerate}
		\item Prove that $\sqrt3$ is irrational. Prove that $\sqrt4$ is irrational. \solutionspace{2cm} 
		\item Prove that there is no smallest rational number greater than 0. \solutionspace{2cm}
		\item Prove that there is no greatest prime. \solutionspace{4cm}
	\end{enumerate}
	%\hrule
	\paragraph{Proof by Exhaustion} These proofs rely on verifying that the statement is true for all cases.
	\begin{enumerate}
		\item Prove that $(n+1)^3 \geq 3^n$ for $n\in \mathbb{N}, n\leq4$.\solutionspace{1cm}
		\item Prove that no perfect square ends with an 8. \solutionspace{2cm}
	\end{enumerate}
	\hrule
	\paragraph{Nonconstructive Proof} A proof which shows that something is true without providing a method for finding a specific example.
	\begin{enumerate}
		\item Prove that for $f(x)=x^3-3x^2+2x-4$ there exists a real $r, 2<r<3$ such that $f(r)=0$. \solutionspace{2cm}
	\end{enumerate}
	\hrule
	\paragraph{Proof by Induction} A proof that shows that if the statement is true for some case, then it must be true for all other cases related to that case.
	\begin{enumerate}
		\item Prove that $x(x+1)(x+2)$ is always divisible by 3. \solutionspace{1cm}
		\item Prove that $a^n-1$ is always divisible by $a-1$ for $a,n \in \mathbb{N}$. \solutionspace{2cm}
		\item Prove that $n!>2^n$ for $n\in\mathbb{N}, n\geq4$.
	\end{enumerate}
\end{document}