\input{../PresentationPreamble}

\usepackage{adjustbox}
\usepackage{wrapfig}
\usepackage{textpos}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usetikzlibrary{angles,quotes}
\usetkzobj{all}

\title{Euclid Preparation 4}
\subtitle{Proofs}
\author{Lev Raizman}
\institute{William Lyon Mackenzie C.I. Math Club}
\date{\copyright{} Lev Raizman, 2018}

\begin{document}
	\frame{\titlepage}
	\section{Direct Proof}
	%\if{false}
	\begin{namedframe}{What is it?}
		A direct proof it the most basic type of proof.
		\sep
		It follows a set of logically true statements, which allow one to arrive from statement A to statement B.
		\sep
		They can rely on axioms, definitions, and earlier proved COMMON KNOWLEDGE theorems.
		\sep
		Proof by example is a sub-category of direct proofs, and is not covered in this lesson. It consists of finding a single case to a supposition in the form of ``There exists $N$ such that ...''.
	\end{namedframe}
	\input{./Definitions}
	\input{./ExamplesDirectProof}
	%\fi
	\section{Proof by Contradiction}
	%\if{false}
	\begin{namedframe}{What is it?}
		A proof by contradiction is another common method of proving a statement.
		\sep
		It makes an assumption, and then follows through a set of logical steps that show that if the assumption is true, the assumption must be false. This results in a contradiction, meaning the assumption is false.
		\sep
		A similar style of proof is called ``Proof by Contraposition'', which proves a statement ``If $A$ then $B$'' by proving that ``If not $A$, then not $B$''.
	\end{namedframe}
	\input{./ExamplesContradictProof}
	%\fi
	\section{Proof by Exhaustion}
	%\if{false}
	\begin{namedframe}{What is it?}
		This proof is a case by case proof, but must be used with caution.
		\sep
		It splits the question into all the possible cases, and then proves that the statement is true for all possible cases.
		\sep
		It can look very disorganized, especially if the cases are singular numbers instead of sets, but it is still a proof.
	\end{namedframe}
	\input{./ExamplesExhaustProof}
	%\fi
	\section{Nonconstructive Proof}
	%\if{false}
	\begin{namedframe}{What is it?}
		This proof is quite rare, and is somewhat similar to an exhaustive proof
		\sep
		It relies on showing that within a given set of parameters something must be possible, without pinpointing exactly what it is. This is why it is called nonconstructive.It also often relies on exhaustive properties of these parameters.
		\sep
		It is also sometimes called ``Proof by Ternary Exclusion'', when there are two cases, and no third one is possible.
	\end{namedframe}
	\input{./ExamplesNonConProof}
	%\fi
	\section{Proof by Induction}
	%\if{false}
	\begin{namedframe}{What is it?}
		This proof is extremely versatile, and should be applied if possible.
		\sep
		It relies on proving a case, then assuming that the statement is true, and proving that the statement is always true for an input one greater or one less. This results in a recursive proof of all other values.
		\sep
		Despite its name, the proof is still deductive, not inductive.
	\end{namedframe}
	\input{./ExamplesInductiveProof}
	%\fi
\end{document}